Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2018-12-03 paper/ms.tex
Added a new version of Carlyn's figure.
Wee update of Carlyn's paper.

Supernovae are classified observationally 
by their light curves and spectra~~\citet{minkowski41,bertola64,porterfilippenko87,
wheelerharkness1990conf,Fili97}, with the type Ia designation following from
the absence of H in the spectrum and the presence of a specific Si 
line~\citep{filippenko:optical,hillebrandt.niemeyer:type}. These events
have been associated with C burning under degenerate conditions
for some time~\citep{hoylefowler60,arnett.truran.ea:nucleosynthesis},
but discerning the setting(s) of these events is proving difficult
and remains the subject of active research. At present there are three
widely-accpeted scenarios: the {\em single degenerate} scenario,
the {\em double detonation} or {\em sub-Chandrasekhar} scenario, 
the {\em white dwarf merger} or {\em double degenerate} scenario.

@@

The white dwarf merger progentor picture has two white dwarfs 
coming together and subsequently exploding~\citep{webbink84,ibentutukov84}.

. This scenario 
provides an abundance of degenerate fuel, which may explain some 
The other main class of models is the DD progenitor,
\citep{webbink84,ibentutukov84}, in which two WDs inspiral and merge.
This scenario includes inspiraling pairs, collisions, violent mergers,
and also the ``core-degenerate'' model where the merger takes place in
a common envelope
\citep{raskinetal2009,pakmoretal2011,kashi:2011,pakmoretal2012a,Shenetal12}
Also
see~\citet{hillebrandt.niemeyer:type,howell2011,hillebrandtetal2013,calderetal2013}
for additional discussion.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_yield_vs_mass_at_high_dens.png}
\caption{\label{fig:masshighdens}
...
}
\end{figure}

>>>>

Supernovae are classified observationally 
by their light curves and spectra~\citep{minkowski41,bertola64,porterfilippenko87,
wheelerharkness1990conf,Fili97}, with the type Ia designation following from
the absence of H in the spectrum and the presence of a specific Si 
line~\citep{filippenko:optical,hillebrandt.niemeyer:type}. These events
have been associated with C burning under degenerate conditions
for some time~\citep{hoylefowler60,arnett.truran.ea:nucleosynthesis},
but discerning the setting(s) of these events is proving difficult
and remains the subject of active research. At present there are three
widely-accpeted scenarios: the {\em single degenerate} scenario,
the {\em double detonation} or {\em sub-Chandrasekhar} scenario, 
the {\em white dwarf merger} or {\em double degenerate} scenario.

@@

The white dwarf merger progentor picture has two white dwarfs 
coming together and subsequently exploding~\citep{webbink84,ibentutukov84}.
This scenario provides an abundance of degenerate fuel, which may explain some 
bright events~\citep{scalzo:2010,Yuan:2010}. White dwarf mergers  scenario

The other main class of models is the DD progenitor,
\citep{webbink84,ibentutukov84}, in which two WDs inspiral and merge.
This scenario includes inspiraling pairs, collisions, violent mergers,
and also the ``core-degenerate'' model where the merger takes place in
a common envelope
\citep{raskinetal2009,pakmoretal2011,kashi:2011,pakmoretal2012a,Shenetal12}
Also
see~\citet{hillebrandt.niemeyer:type,howell2011,hillebrandtetal2013,calderetal2013}
for additional discussion.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_yield_vs_mass_at_high_dens_v2.png}
\caption{\label{fig:masshighdens}
...
}
\end{figure}
